Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-03-30 Report/convergence_centralized.tex
latest changes

To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are satisfied by the centralized formulations.
\begin{itemize}
	\item[(a)] The function should be bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence of the objective values should be decreasing in each iteration
	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
\end{itemize}
The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm. Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point. Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Theorem 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum. Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limiting point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

\subsection{Bounded Objective Function and Compact Feasible Set}
The feasible set of the problem \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which can be verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, and therefore, a compact set.

@@

\subsection{Monotonicity of the Objective Function} \label{mcity}
To show the objective decreases monotonically in each iteration, we need to have a nonincreasing objective values in each \ac{SCA} update and also in each \ac{AO} update. To prove this, let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{subeqnarray} \label{con}
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \slabel{con-obj} \\
	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \slabel{con-dc} \\
	&\quad& g_1(\mx,\my) \leq 0 \eqsub \slabel{con-cvx-blk} \\
	&\quad& g_2(\mx) \leq 0 \eqsub \slabel{con-cvx}
\end{subeqnarray}
where \me{g_2,f} are convex and \me{h} is a linear function. Let \me{g_0,g_1} be convex in either \me{\mx} or \me{\my} but not on both. The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}. Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\iftoggle{single_column}{
\begin{equation}
\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{equation}
}{
\begin{align}
\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
								 & \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{align}}

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of varibles and optimize for others \cite{bezdek2002some}. In \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint \eqref{con-dc}. We adopt \ac{SCA} presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}. As the \ac{SCA} iteration converges, let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration. Let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iterate for a fixed \me{\my}.

@@

\me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution in the \me{\ith{k}} iteration. The point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function, is also feasible for \eqref{con-m} using the following inequality

@@

Using \eqref{con-sub-set}, we can show that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{i-1}} \ac{AO} iteration. At each \ac{SCA} update, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,quoc2011sequential}

@@

Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches a limiting point as \me{k \rightarrow \infty}. The equality in \eqref{con-convergence} is achieved when the objective converges. The feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not be a stationary point of \eqref{con}, since it is a minimizer in the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.

Once the solution is found for a fixed \me{\my}, \me{\my} is optimized by fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}}. Even after treating \me{\mx} as a constant, the problem is still nonconvex due to the \ac{DC} constraint. Following similar approach, we can find the minimizer \me{\iter{\my}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} for a similar convex subproblem \eqref{con-m} at each iteration \me{{k}}. Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration. The convergence and the nonincreasing behavior of the objective follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.}. Now, the solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}. Note that the limiting point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.

@@

When the objective is zero, the uniqueness of the transmit precoders are not guaranteed by the constraints \eqref{eqn-8} and \eqref{eqn-mse-1.3}, since they are the under-estimators and need not be active at the minimum. To obtain a unique set of transmit precoders and the receive beamformers in all cases, we can regularize the objective with a strongly convex function as
\begin{equation}
\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
\end{equation}
where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant to make the objective strongly convex. The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration. %Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}. The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations. When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems. To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.

\subsection{Convergence of the Beamformer Iterates} \label{c-b}
So far, we have considered the convergence of the objective sequence. In this section, we discuss the convergence of the beamformer iterates generated by the iterative algorithm for \eqref{con} using \cite{zangwill1969nonlinear,meyer1976sufficient}. Let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point in the \eqn{\ith{i}} \ac{AO} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.}. Let \me{\mc{A}} be the point-to-set mapping algorithm defined as
\begin{equation}
\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}.
\end{equation}
Since the algorithm finds a unique solution in each iteration, the mapping denoted by  \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}. Let \me{\mc{F}^\ast \subset \mc{F}} be the set of fixed points, \textit{i.e}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.

By using \cite[Theorem 3.1]{meyer1976sufficient}, we can show the convergence of beamformer iterates to a fixed point as follows.
\begin{itemize}
\item The function \me{f} in \eqref{con-m} should continuous and bounded.
\item The feasible set \me{\iter{\mc{Y}}{\ast}{i}} for each iteration should be compact.
\item The sequence \me{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} should be strictly monotonic with respect to the objective function \me{f}, \textit{i.e}, \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
\end{itemize}
Note that the above conditions are satisfied by the proposed algorithm and the strict monotonicity can also be verified from \eqref{fixed_point}. Using \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}, we can show that (i) all limiting points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}. The algorithm \me{\mc{A}} finds a unique solution in each iteration, \textit{i.e}, \me{\mc{F}^\ast = \{\ma^\ast\}}, which is a limiting point.

@@

\subsection{Stationary Points of the Nonconvex Problem}
To show the stationarity of the fixed points in \me{\mc{F}^\ast}, it must satisfy the \ac{KKT} conditions of \eqref{con}. As \me{i \rightarrow \infty}, it satisfies
\iftoggle{single_column}{
\begin{equation} \label{con-opt}\allowdisplaybreaks
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) = 
f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
\end{equation}}{
\begin{multline} \label{con-opt}\allowdisplaybreaks
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
\end{multline}}
where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. Using \cite[Theorem 10]{lanckriet2009convergence} and \cite[Theorems 2,11]{scutari_1}, we can show that the fixed point is a stationary point of the nonconvex problem \eqref{con}. Since the feasible point  \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} for \me{\mc{A}} under the mapping \me{f} \cite{meyer1976sufficient}, it is a stationary point of \eqref{con} over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. The feasible point need not be a local optimum for the nonconvex problem unless all the constraints are inactive, \textit{i.e}, if the solution is inside the feasible set \me{\mc{F}}. In this scenario, the Lagrange multipliers are all zero to satisfy the complementary slackness criterion, and therefore, the solution point is a local optimum of the non convex problem in \eqref{con}.

>>>>

To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are satisfied by the centralized formulations.
\begin{itemize}
	\item[(a)] The function should be bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence of the objective values should be decreasing in each iteration
	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
\end{itemize}
The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm. Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point \cite{meyer1976sufficient}. Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th. 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum. Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limiting point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

\subsection{Bounded Objective Function and Compact Feasible Set}
The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which can be verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, and therefore, a compact set.

@@

\subsection{Monotonicity of the Objective Sequence} \label{mcity}
In this section, we show the nonincreasing behavior of the objective values in each \ac{SCA} and \ac{AO} update. Let us consider a general formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{subeqnarray} \label{con}
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \slabel{con-obj} \\
	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \slabel{con-dc} \\
	&\quad& g_1(\mx,\my) \leq 0 \eqsub \slabel{con-cvx-blk} \\
	&\quad& g_2(\mx) \leq 0 \eqsub \slabel{con-cvx}
\end{subeqnarray}
where \me{g_2,f} are convex and \me{h} is a linear function. Let \me{g_0,g_1} be convex in either \me{\mx} or \me{\my} but not on both. The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}. Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\iftoggle{single_column}{
\begin{equation}
\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{equation}
}{\begin{align}
\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
								 & \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{align}}

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of varibles and optimize for others \cite{bezdek2002some}. In \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint \eqref{con-dc}. We adopt \ac{SCA} presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}. Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when the \ac{SCA} iteration converges in the \me{\ith{i}} \ac{AO} iteration and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iteration for a fixed \me{\my}.

@@

\me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution in the \me{\ith{k}} iteration. The point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function satisfies

@@

Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{i-1}} \ac{AO} iteration. At each \ac{SCA} update, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,quoc2011sequential}

@@

Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches a limiting point of the \ac{SCA} as \me{k \rightarrow \infty}. The equality in \eqref{con-convergence} is achieved upon the \ac{SCA} convergence. The feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not to be a stationary point of \eqref{con}, since it is a minimizer over the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}.

Once the solution is found for a fixed \me{\my}, it is then optimized by fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}}. Even after treating \me{\mx} as a constant, the problem is nonconvex due to the \ac{DC} constraint. Following similar approach as above, we can find a minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} for a similar convex subproblem \eqref{con-m} at each iteration \me{{k}}. Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration. The convergence and the nonincreasing behavior of the objective follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.}. The limiting point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.

@@

When the objective is zero, the uniqueness of the transmit precoders are not guaranteed by the constraints \eqref{eqn-8} and \eqref{eqn-mse-1.3}, since they are the under-estimators and need not be active at the minimum. To obtain a unique set of transmit precoders and the receive beamformers in all cases, we can regularize the objective with a strongly convex function as
\begin{equation}
\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
\end{equation}
where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant. The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration. %Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}. The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations. When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems. To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.

\subsection{Convergence of the Beamformer Iterates} \label{c-b}
So far, we have considered the convergence of the objective sequence. In this section, we discuss the convergence of the beamformer iterates generated by the iterative algorithm for \eqref{con} using \cite{zangwill1969nonlinear,meyer1976sufficient}. Let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point in the \eqn{\ith{i}} \ac{AO} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.}. Let \me{\mc{A}} be the point-to-set mapping algorithm defined as
\begin{equation} \label{algorithm_fixed}
\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}.
\end{equation}
Since the algorithm finds a unique solution in each iteration, the mapping denoted by  \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}. Let \me{\mc{F}^\ast \subset \mc{F}} be the set of fixed points, \textit{i.e}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.

Using \cite[Th. 3.1]{meyer1976sufficient}, convergence of the iterates to a fixed point can be shown, if the following conditions are satisfied.
\begin{itemize}
\item Objective function \me{f} should be bounded and continuous.
\item The feasible set \me{\iter{\mc{Y}}{\ast}{i}} in each iteration should be compact.
\item The sequence \me{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} should be strictly monotonic with respect to the objective function \me{f}, \textit{i.e}, \me{\ma^\prime = \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
\end{itemize}
Note that the above conditions are satisfied by the proposed algorithm \me{\mc{A}} in \eqref{algorithm_fixed} and the strict monotonicity can also be verified from \eqref{fixed_point}. Using \cite{zangwill1969nonlinear} and \cite[Th. 3.1]{meyer1976sufficient}, we can show that (i) all limiting points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}. Even though the fixed points in the set \me{\mc{F}^\ast} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limiting point, \textit{i.e}, \me{\mc{F}^\ast = \{\ma^\ast\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.

@@

\subsection{Stationary Points of the Nonconvex Problem}
To show the limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}. As \me{i \rightarrow \infty}, the objective converges as
\iftoggle{single_column}{
\begin{equation} \label{con-opt}\allowdisplaybreaks
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) = 
f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
\end{equation}}{
\begin{multline} \label{con-opt}\allowdisplaybreaks
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
\end{multline}}
where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is the limiting point of \me{\mc{A}} for a given initial point. As discussed in Appendix \ref{c-b}, the unique limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a fixed point of \me{\mc{A}}. Using \cite[Th. 10]{lanckriet2009convergence} and \cite[Th. 2 and 11]{scutari_1}, we can show that the fixed points obtained by the algorithm \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}. It can be verified by writing the \ac{KKT} expressions for the original problem in \eqref{con} and the relaxed one in \eqref{con-m} at the limiting point \eqref{con-opt}, by using the linear relaxation \eqref{con-relax} for the nonconvex constraint \cite{marks1978technical}.

### 2015-03-30 Report/convergence_distributed.tex
latest changes

Unlike the primal or the \ac{ADMM} methods, the decomposition via \ac{KKT} conditions for the \ac{MSE} reformulation discussed in Section \ref{sec-4.3}, all variables are updated at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method. It is not guaranteed to obtain the same point as that of the centralized problem.

@@

To avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence. Even though the optimization variables are updated together, the monotonicity of the objective still follows from the arguments presented in Appendix \ref{mcity}. Using the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}, the convergence to a stationary point of the nonconvex problem in \eqref{eqn-6} can be guaranteed for the proposed distributed algorithm with the \me{\ell_2} norm. It is also verified in all the numerical experiments considered in Section \ref{sec-5.2}.

\begin{comment}
The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5} if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution. Since the subproblem in \eqref{eqn-decent-1} is convex, each \ac{BS} specific slave subproblem is also convex for a fixed interference vector \me{\mbfa{\zeta}_{b_k}^{(i)}} \cite{palomar2006tutorial}. The master subproblem in the \acl{PD} uses subgradient to update the coupling interference vectors in consensus with the objective function, it is guaranteed to converge to the centralized solution as the iteration \me{i \rightarrow \infty} \cite{bertsekas1999nonlinear} for a diminishing step size. It can be seen that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and the set is compact.

>>>>

Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions for the \ac{MSE} reformulation in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method. Therefore, it is not guaranteed to obtain the same point as that of the centralized problem.

@@

To avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence. Since the optimization variables are updated together, it is difficult to prove the monotonicity of the objective in each block update. Therefore, it is difficult to prove the convergence of the Algorithm \ref{algo-4} to a stationary point of the original nonconvex problem in \eqref{eqn-mse-1}. Even though the convergence is not theoretically guaranteed, it converges in all numerical experiments considered in Section \ref{sec-5.2}.

\begin{comment}
%Even though the optimization variables are updated together, the monotonicity of the objective still follows from the arguments presented in Appendix \ref{mcity}. Using the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}, the convergence to a stationary point of the nonconvex problem in \eqref{eqn-6} can be guaranteed for the proposed distributed algorithm with the \me{\ell_2} norm. It is also verified in all the numerical experiments considered in Section \ref{sec-5.2}.

The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5} if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution. Since the subproblem in \eqref{eqn-decent-1} is convex, each \ac{BS} specific slave subproblem is also convex for a fixed interference vector \me{\mbfa{\zeta}_{b_k}^{(i)}} \cite{palomar2006tutorial}. The master subproblem in the \acl{PD} uses subgradient to update the coupling interference vectors in consensus with the objective function, it is guaranteed to converge to the centralized solution as the iteration \me{i \rightarrow \infty} \cite{bertsekas1999nonlinear} for a diminishing step size. It can be seen that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and the set is compact.
